|

### 2021-11-18 01-Chp-Background.Rmd
End of day:

@@

I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading). Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
<!----------------------------------------------------------------------------->

@@

* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions

>>>>

<!-- TODO Consider inverting the order so that triangulation comes last - as it does in the thesis as a whole! -->

@@

I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading). Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.

@@

* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions
* To propose a generalised framework for the quantitative triangulation across diverse evidence sources

### 2021-11-18 05-Chp-CPRD-Analysis.Rmd
End of day:

We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.

@@

We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementias, and a composite all-cause dementia outcome. When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Figure \@ref(fig:decisionTreeFig)). The diagnosis date of the outcome was determined by the first record of a relevant code.

>>>>

I considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.

@@

I considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementias, and a composite all-cause dementia outcome. When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Figure \@ref(fig:decisionTreeFig)). The diagnosis date of the outcome was determined by the first record of a relevant code.
